Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-03-03 paper/paper1/ms.tex
Re-ran the cloning with way more training steps, fixed RV offset.  Looks great!

\begin{figure}[hbt!]
 \centering
 \includegraphics[width=0.8\textwidth]{figures/blase_clone_demo.png}
 \caption{PHOENIX spectrum cloned with blas\'e.  This $T_{\mathrm{eff}}=4100\;$K,  $\log{g}=3.5$ solar metallicity model has over 5,000 individual cloned spectral lines.  The figure zooms in on a $0.7\%$ portion of the large spectral bandwidth that was cloned.  Some conspicuous flaws can be seen near the wings of broad lines, or surrounding blended lines.  Some initialization effects can be seen in this example, suggesting that the cloning procedure requires additional training iterations to achieve the best performance.}
 \label{fig_cloned_spectrum_demo}
\end{figure}

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_clone_demo.png}
    \caption{PHOENIX spectrum cloned with blas\'e.  This $T_{\mathrm{eff}}=4100\;$K,  $\log{g}=3.5$ solar metallicity model has 11,759 individual cloned spectral lines, each with 3 tuned parameters.  The pictured 25 \AA chunk contains 73 spectral lines and represents a mere $<0.7\%$ portion of the entire spectral bandwidth that was cloned.  Some flaws can be seen near the cores of deep lines, or wings of broad lines.}
    \label{fig_cloned_spectrum_demo}
\end{figure}
